Contextuality and the Born Rule in Fuzzy Quantum Theories

### 2017-03-15 prop_letter.tex
prop_letter.tex \begin{abstract} Updating...

\begin{abstract}
\begin{description}
\item[Background] This paper wants to understand the quantum measurement in the
bounded resource.
\item[Purpose] ?
\item[Method] We replace quantum real-valued probability measures by
interval-valued ones whose range can be restricted to finite number of
intervals representing finite precision measurement.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
found some legitimate quantum interval-valued probability measures which cannot
be explained by the Born rule.
\item[Conclusions] Our research provide a new insight of the role of finite
precision measurement when formulate quantum theory.
\end{description}
\end{abstract}

>>>>

\begin{abstract}
\begin{description}
\item[Background] In a world of bounded resource, the quantum theory should
base on only finite precision measurement.
\item[Purpose] This paper wants to understand the finite precision quantum
measurement.
\item[Method] We replace quantum real-valued probability measures by
interval-valued ones whose range can be restricted to finite number of
intervals.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
found some legitimate quantum interval-valued probability measures which cannot
be explained by the Born rule.
\item[Conclusions] Our research provides a new insight of the role of
measurement when formulating quantum theory.
\end{description}
\end{abstract}
